%%
%% Date: 22 Mar 2022
%%
%%
\documentclass[12pt]{book}
%%
\usepackage{xspace}
\usepackage{url}
%%
\usepackage{graphicx}
%%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage[all,cmtip]{xy}
%%
\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%%
\usepackage{xcolor}
%%
\usepackage{makeidx}
%%
\graphicspath{{./figures}}
%%
\makeindex
%%
%% ----------------------------------------------------------------------
\begin{document}


%% ----------------------------------------------------------------------
\chapter{Outline}

\section{Introduction}

\begin{itemize}
\item Simulation science: what does this mean? This may be a question
  to tie all topics together and help motivate the topics of the book,
  and/or put it into a good context.
  \begin{itemize}
  \item A real system along with questions from e.g. policy makers;
  \item Formal models of the systems and their components; modeling for
    required scale and resolution; modeling for rapid response/near real-time;
  \item ``Real'' data about the system (e.g., historical, structural,
    procedural);
  \item What to do when no data is available or scenarios are
    hypothetical or have never taken place. Synthetic data. Data quality.
  \item Integration/harmonization of (formal) models;
  \item Model validation;
  \item Model implementation and verification; modules/simulation
    models; software practices and standards;
  \item Separation of models and modules, and why this is
    important. And why it does not always happen.
  \item Module integration and computational architecture; re-visiting
    scaling; architecture; the role of testing;
  \item Scientific reproducibility: what does this mean for simulation
    science? open/closed source; open/closed data; proprietary data;
  \item Computational validation: a two-step inference: modules
    faithfully represent model \& model faithfully represents reality;
    and the trouble that agreeing with other models does neither
    really validate the current model (or those other models);
  \item Statistical designs
  \item Analytics;
  \item Data quality - again
  \item Some kind of brief summary; maybe a figure/diagram pulling the pieces together;
  \end{itemize}
\item Overview of what the book is about;
\item Relevance: for systems that are (or are in need of) being
  analyzed nowadays (networked);
\item Gap in the literature;
\item Prepare list of related literature, e.g.,~\cite{Law:07}. This
  may be somewhat tricky, so it may useful to state something about
  what we choose to focus on while acknowledging examples that we do
  not address (possible example: Petri Nets type work);
\item Contrast with ``continuous'' modeling and analysis; make the
  point that models that are ``continuous'' may also be part of what
  we are covering;
\item Book companion web site;
\item Aspects that will help adoption for courses;
\end{itemize}

%% ----------------------------------------------------------------------
\section{Examples of (real) systems}

\begin{itemize}
\item An example to be used throughout the book;
\item NPS-1;
\end{itemize}

%% ----------------------------------------------------------------------
\section{Formal modeling framework}

\begin{itemize}
\item Why?
\item The ``implementation defines the model'' pitfall
\item Graph dynamical systems
  \begin{itemize}
  \item Why GDS? As a minimum, provides a precise + conceptual
    framework suited for modeling networked systems
  \item Analysis types: mathematical, computational, numerical,
    game-theoretic
  \end{itemize}
\item Validation and verification; sensitivity analysis;
\end{itemize}

%% ----------------------------------------------------------------------
\section{Synthetic populations and digital twins}

\begin{itemize}
\item Why?
\item Examples. Our work; industry;
\item How in general?
\item Synthetic populations
\item Synthetic, electrical distribution networks;
\end{itemize}


%% ----------------------------------------------------------------------
\section{Unencapsulated agency}

\begin{itemize}
\item Central idea; coordinate system(s);
\item Examples;
\item System factorization/decomposition; validity;
\end{itemize}
%


% ----------------------------------------------------------------------
\section{Architecture design}

\index{architecture}

\begin{itemize}
\item What is it? Mapping models to software (aka modules);
\item The fact that this is a non-trivial but central aspect;
\item Construction of modules from system components;
\item Coordinating architecture and module contracts; integration of metrics;
\item Computing environment;
\item Designing for scaling; (what does the scenario/application
  require in terms of scale?)
\item Data management; (e.g., communcation among modules; provenance)
\item Scientific reproducibility;
\item Verfication and validation; integration of tests within framework;
\item System testing harnesses;
\item SciDuct;
\end{itemize}

%% ----------------------------------------------------------------------
\chapter{Introduction}

Starts here ...


%% ----------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{references}
%% ----------------------------------------------------------------------
\printindex
%% ----------------------------------------------------------------------
\end{document}
